---
title: "lexicon_analysis"
author: "Anders Hjulmand"
date: '2022-09-03'
output: html_document
---

We load Libraries
```{r}
pacman::p_load(tidyverse, wesanderson, patchwork, psych, xlsx, lme4, textdata, textstem, geomtextpath, ggcorrplot)
```

We define a color palette for plots
```{r}
color_palette <- c(wes_palette("Darjeeling1")[2], wes_palette("Darjeeling1")[3])
```

And load data:
```{r}
data_long <- read_csv("Data/data_long.csv") %>% 
  rename('Valence_VAD' = 'Valence.x',
         'Arousal_VAD' = 'Arousal.x',
         'Dominance_VAD' = 'Dominance'
         ) %>% 
  mutate(Dem = as.factor(Dem),
         Depressed = as.factor(Depressed),
         Anxiety = as.factor(Anxiety),
         Dem = fct_relevel(Dem, 'this', 'that'),
         Depressed = fct_relevel(Depressed, '0', '1'),
         Anxiety = fct_relevel(Anxiety, '0', '1'))

#targets <- read_csv("Data/target.csv") %>% 
  #select(ID, F1, F2, F1_transformed, F2_transformed, Depressed_F1, Anxiety_F2)

#data_long <- left_join(data_long,
#                       targets,
#                       by = 'ID'
#) %>% 
#  mutate(Dem = as.factor(Dem),
#         Depressed_F1 = as.factor(Depressed_F1),
#         Anxiety_F2 = as.factor(Anxiety_F2),
#         Dem = fct_relevel(Dem, 'this', 'that'),
#         Depressed_F1 = fct_relevel(Depressed_F1, '0', '1'),
#         Anxiety_F2 = fct_relevel(Anxiety_F2, '0', '1'))
```


# Data Wrangling

Here we make the target values: the difference in proportion proximal demonstrative between patients and non-patients for each word.

## Depressed/Non-depressed
```{r}
#each group answered the same words
#divide each participant into depressed/non-depressed
#for each participant for each word, measure proportion this/that 
```

```{r}
#depressed non depressed
data_long %>% 
  group_by(Depressed) %>% 
  tally()
```

```{r}
#count of this that for each word between depressed/non-depressed
te <- data_long %>% 
  filter(Depressed == 0 | Depressed == 1) %>% 
  group_by(Word, Depressed, Dem) %>% 
  tally()


te %>% 
  ggplot() +
  aes(x=n, fill=Dem) + 
  geom_density(alpha = 0.5) + 
  theme_minimal() +
  facet_wrap(~Depressed)

#hvad viser den her egentlig? 

te %>% 
  ggplot() + 
  aes(x=n, fill = Depressed) + 
  geom_density(alpha = 0.8) + 
  theme_minimal()
```


```{r}
#proprotion of this/that for depressed/non-depressed for each word
word_depr_proportion <- tibble()

i = 1
for (row in seq(1, by=2, len=(length(unique(te$Word))*2))) {
    prop = te$n[row]/(te$n[row]+te$n[row+1]) 
    output = c(as.character(te$Word[row]), as.character(te$Depressed[row]), prop)
    word_depr_proportion <- rbind(word_depr_proportion, output)
    i = i + 1
}

word_depr_proportion <- word_depr_proportion %>% 
  rename('Word' = colnames(word_depr_proportion[1]),
         'Depressed' = colnames(word_depr_proportion[2]),
         'Proportion' = colnames(word_depr_proportion[3])) %>% 
  mutate(#Word = as.factor(Word),
         #Depressed_F1 = as.factor(Depressed_F1),
         Proportion = as.numeric(Proportion))

word_depr_proportion %>% 
  ggplot() +
  aes(x=Proportion, fill = Depressed) + 
  geom_density(alpha = 0.5) + 
  theme_minimal()
```


```{r}
#difference proportion this/that for depressed/non-depressed for each word
word_depr_diff <- tibble()

i = 1
for (row in seq(1, by=2, len=length(unique(te$Word)))) {
    diff = word_depr_proportion$Proportion[row]-word_depr_proportion$Proportion[row+1] 
    output = c(as.character(word_depr_proportion$Word[row]), diff)
    word_depr_diff <- rbind(word_depr_diff, output)
    i = i + 1
}

word_depr_diff <- word_depr_diff %>% 
  rename('Word' = colnames(word_depr_diff[1]),
         'proportion_diff_depr' = colnames(word_depr_diff[2])) %>% 
  mutate(Word = as.factor(Word),
         proportion_diff_depr = as.numeric(proportion_diff_depr))

word_depr_diff %>% 
  ggplot() + 
  aes(x=proportion_diff_depr) + 
  geom_density() + 
  theme_minimal()

#describe(word_depr_diff$proportion_diff_depr)
```

## Anxiety/Non-Anxiety

```{r}
#anxiety/no-anxiety
data_long %>% 
  group_by(Anxiety) %>% 
  tally()
```

```{r}
#count of this that for each word between anxiety/no-anxiety
te <- data_long %>% 
  filter(Anxiety == 0 | Anxiety == 1) %>% 
  group_by(Word, Anxiety, Dem) %>% 
  tally()


te %>% 
  ggplot() +
  aes(x=n, fill=Dem) + 
  geom_density(alpha = 0.5) + 
  theme_minimal() +
  facet_wrap(~Anxiety)

#hvad viser den her egentlig? 

te %>% 
  ggplot() + 
  aes(x=n, fill = Anxiety) + 
  geom_density(alpha = 0.8) + 
  theme_minimal()
  
```

```{r}
#proprotion of this/that for anxiety/no-anxiety for each word
word_anx_proportion <- tibble()

i = 1
for (row in seq(1, by=2, len=(length(unique(te$Word))*2))) {
    prop = te$n[row]/(te$n[row]+te$n[row+1]) 
    output = c(as.character(te$Word[row]), as.character(te$Anxiety[row]), prop)
    word_anx_proportion <- rbind(word_anx_proportion, output)
    i = i + 1
}

word_anx_proportion <- word_anx_proportion %>% 
  rename('Word' = colnames(word_anx_proportion[1]),
         'Anxiety' = colnames(word_anx_proportion[2]),
         'Proportion' = colnames(word_anx_proportion[3])) %>% 
  mutate(#Word = as.factor(Word),
         #Anxiety = as.factor(Anxiety),
         Proportion = as.numeric(Proportion))

word_anx_proportion %>% 
  ggplot() +
  aes(x=Proportion, fill = Anxiety) + 
  geom_density(alpha = 0.5) + 
  theme_minimal()
```


```{r}
#difference proportion this/that for anxiety/no-anxiety for each word
word_anx_diff <- tibble()

i = 1
for (row in seq(1, by=2, len=length(unique(te$Word)))) {
    diff = word_anx_proportion$Proportion[row]-word_anx_proportion$Proportion[row+1] 
    output = c(as.character(word_anx_proportion$Word[row]), diff)
    word_anx_diff <- rbind(word_anx_diff, output)
    i = i + 1
}

word_anx_diff <- word_anx_diff %>% 
  rename('Word' = colnames(word_anx_diff[1]),
         'proportion_diff_anx' = colnames(word_anx_diff[2])) %>% 
  mutate(Word = as.factor(Word),
         proportion_diff_anx = as.numeric(proportion_diff_anx))

word_anx_diff %>% 
  ggplot() + 
  aes(x=proportion_diff_anx) + 
  geom_density() + 
  theme_minimal()

#describe(word_anx_diff$proportion_diff_anx)
```


## Merging with VAD and NRC emotion

Merge with VAD dataset for both depression and anxiety.
```{r}
#for depression
word_diff_VAD <- left_join(
  word_depr_diff,
  data_long[, c('Word', 'Valence_VAD', 'Arousal_VAD', 'Dominance_VAD')],
  by = 'Word'
) %>% distinct()

# see which words are not in the VAD dataset
py <- word_diff_VAD %>% 
  filter(is.na(Valence_VAD))

#filter words in our dataset that is not in the VAD dataset (17 Words)
word_diff_VAD <- word_diff_VAD %>% 
  filter(!(Word %in% py$Word))

#Lastly we add anxiety proportion diff
word_diff_VAD <- left_join(
  word_diff_VAD,
  word_anx_diff,
  by = 'Word'
)
word_diff_VAD <- word_diff_VAD  %>% relocate(Word, proportion_diff_depr, proportion_diff_anx)
```

Merge with NRC emotion lexicon (binary lexicon)
```{r}
#for depression
word_diff_emotion <- left_join(
  word_depr_diff,
  data_long[, c('Word', 'anger', 'anticipation', 'disgust', 'fear', 'joy', 'negative', 'positive', 'sadness', 'surprise', 'trust')],
  by = 'Word'
) %>% distinct()

# see which words are not in the emotion dataset
py <- word_diff_emotion %>% 
  filter(is.na(anger))

#filter words in our dataset that is not in the emotion dataset (93 words)
word_diff_emotion <- word_diff_emotion %>% 
  filter(!(Word %in% py$Word))

#Lastly we add anxiety proportion diff
word_diff_emotion <- left_join(
  word_diff_emotion,
  word_anx_diff,
  by = 'Word'
)
word_diff_emotion <- word_diff_emotion  %>% relocate(Word, proportion_diff_depr, proportion_diff_anx)
```

Lastly we add group number to both lexicons and save them
```{r}
word_diff_VAD <- left_join(word_diff_VAD,
                           data_long %>% select(Word, Group) %>% distinct(),
                           by = 'Word') %>% relocate(Word, Group)

word_diff_emotion <- left_join(word_diff_emotion,
                           data_long %>% select(Word, Group) %>% distinct(),
                           by = 'Word') %>% relocate(Word, Group)


#write.csv(word_diff_VAD, 'Data/lexicon_analysis/word_diff_VAD_raw_scores.csv')
#write.csv(word_diff_emotion, 'Data/lexicon_analysis/word_diff_emotion_raw_scores.csv')
```


# Python code

------------------------Python code------------------------
running python code from script lexicon_analysis.ipynb
----------------------------------------------------------- 


#Loading Datasets
```{r}
word_diff_VAD <- read_csv('Data/lexicon_analysis/word_diff_VAD_raw_scores.csv')
word_diff_emotion <- read_csv('Data/lexicon_analysis/word_diff_emotion_raw_scores.csv')
word_diff_combined <- read_csv('Data/lexicon_analysis/word_diff_combined_raw_scores.csv')
```



# Analysis for VAD
```{r}
de <- word_diff_VAD %>% 
  gather(c(6,7,8),
         key = 'dimension',
         value = 'value') %>% 
  ggplot() + 
  aes(x=value, y=proportion_diff_depr) + 
  geom_point(aes(color = dimension)) + 
  stat_smooth(method = 'lm',
              color = 'black',
              size = 0.7) +
  facet_wrap(~dimension) + 
  theme_minimal() + 
  theme(legend.position = 'none') + 
  labs(title= 'Depression')

an <- word_diff_VAD %>% 
  gather(c(6,7,8),
         key = 'dimension',
         value = 'value') %>% 
  ggplot() + 
  aes(x=value, y=proportion_diff_anx) + 
  geom_point(aes(color = dimension)) + 
  stat_smooth(method = 'lm',
              color = 'black',
              size = 0.7) +
  facet_wrap(~dimension) + 
  theme_minimal() + 
  theme(legend.position = 'none') + 
  labs(title= 'Anxiety')

de/an
```


## Checking colinearity
```{r}
#compute correlation matrix
corr <- round(cor(word_diff_VAD[6:8]), 2)

# Compute a matrix of correlation p-values
p_values <- cor_pmat(word_diff_VAD[6:8])

ggcorrplot(corr,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           colors = c("#6D9EC1", "white", "#E46726"),
           lab = TRUE,
            p.mat = p_values)


#make the partial correlation matrix for depression
hep <- round(partial.r(data = word_diff_VAD,
                 x = c(6,7,8),
                 y = 4, 
                 method = 'pearson'
                 )
             ,2)

#making the correlation plot
plot_depr <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           colors = c("#6D9EC1", "white", "#E46726")) + labs(title = 'Partial Correlation of NRCVAD with target Depression')
           
#make the partial correlation matrix for anxiety
hep <- round(partial.r(data = word_diff_VAD,
                 x = c(6,7,8),
                 y = 5, 
                 method = 'pearson'
                 )
             ,2)

#making the correlation plot
plot_anx <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           colors = c("#6D9EC1", "white", "#E46726")) + labs(title = 'Partial Correlation of NRCVAD with target Anxiety')
           
plot_depr
plot_anx

s

```

# Analysis for emotion lexicon

```{r}
word_diff_emotion %>% 
  gather(c(6:15),
         key = 'dimension',
         value = 'high_low' 
         ) %>% 
  mutate(high_low = as.factor(high_low),
         high_low = recode(high_low, '1' = "High", '0' = "Low")) %>% 
  ggplot() + 
  aes(x=proportion_diff_depr, fill= high_low, label = high_low) + 
  #geom_textdensity(size = 4, fontface = 2, hjust = 0.2, vjust = 0.3) + 
  geom_density(alpha = 0.4) + 
  theme_minimal()+ 
  theme(legend.position = 'bottom') +
  xlim(-0.3,0.3) +
  facet_wrap(~dimension, ncol=2)

word_diff_emotion %>% 
  gather(c(6:15),
         key = 'dimension',
         value = 'high_low' 
         ) %>% 
  mutate(high_low = as.factor(high_low),
         high_low = recode(high_low, '1' = "High", '0' = "Low")) %>% 
  ggplot() + 
  aes(x=proportion_diff_anx, fill= high_low, label = high_low) + 
  #geom_textdensity(size = 4, fontface = 2, hjust = 0.2, vjust = 0.3) + 
  geom_density(alpha = 0.4) + 
  theme_minimal()+ 
  xlim(-0.3,0.3) +
  theme(legend.position = 'bottom') +
  facet_wrap(~dimension, ncol=2)
```


## Checking colinearity
```{r}
#compute correlation matrix
word_diff_emotion <- word_diff_emotion %>% mutate_at(c(5:14), as.numeric)

corr <- round(cor(word_diff_emotion[6:15]), 2)

# Compute a matrix of correlation p-values
p_values <- cor_pmat(word_diff_emotion[6:15])

ggcorrplot(corr,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           colors = c("#6D9EC1", "white", "#E46726"),
           lab = TRUE)


#make the partial correlation matrix for depression
hep <- round(partial.r(data = word_diff_emotion,
                 x = c(6:15),
                 y = 4, 
                 method = 'kendall'
                 )
             ,2)

#making the correlation plot
plot_depr <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           colors = c("#6D9EC1", "white", "#E46726")) + labs(title = 'Partial Correlation of emotion lexicon with target Depression')
           
#make the partial correlation matrix for anxiety
hep <- round(partial.r(data = word_diff_emotion,
                 x = c(6:15),
                 y = 5, 
                 method = 'kendall'
                 )
             ,2)

#making the correlation plot
plot_anx <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           colors = c("#6D9EC1", "white", "#E46726")) + labs(title = 'Partial Correlation of emotion lexicon with target Anxiety')
           
plot_depr
plot_anx

```
# Analysis for combined lexicon of NRCVAD and Emotion Lexicon

```{r}
#word_diff_combined <- left_join(word_diff_emotion,
#                                word_diff_VAD %>% select(-c(proportion_diff_anx,proportion_diff_depr, Group)),
#                                by = 'Word')

# Here we dont lose more words than in the emotion lexicon
#write.csv(word_diff_combined, 'Data/lexicon_analysis/word_diff_combined_raw_scores.csv')
```

## Combined partial correlation matrix

We remove positive and negative from the emotion lexicon, since they are already expressed in Valence from VAD.
```{r}
#compute correlation matrix
word_diff_combined <- word_diff_combined %>% 
  mutate_at(c(6:18), as.numeric)# %>% 
  #select(-c('positive', 'negative'))

corr <- round(cor(word_diff_combined[6:18]), 2)

# Compute a matrix of correlation p-values
p_values <- cor_pmat(word_diff_combined[6:18])

ggcorrplot(corr,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           colors = c("#6D9EC1", "white", "#E46726"),
           lab = TRUE)


#make the partial correlation matrix for depression
hep <- round(partial.r(data = word_diff_combined,
                 x = c(6:18),
                 y = 4, 
                 method = 'kendall'
                 )
             ,2)

#making the correlation plot
plot_depr <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           colors = c("#6D9EC1", "white", "#E46726")) + labs(title = 'Partial Correlation of combined lexicon with target Depression')
           
#make the partial correlation matrix for anxiety
hep <- round(partial.r(data = word_diff_combined,
                 x = c(6:18),
                 y = 5, 
                 method = 'kendall'
                 )
             ,2)

#making the correlation plot
plot_anx <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           colors = c("#6D9EC1", "white", "#E46726")) + labs(title = 'Partial Correlation of combined lexicon with target Anxiety')
           
plot_depr
plot_anx
```

# Results

## VAD
```{r}
VAD_results <- read_csv('Data/lexicon_analysis_performance/VAD_raw_scores.csv')
```

The we load the training and holdout datasets for plotting:
```{r}
VAD_X_train <- read_csv('Data/lexicon_analysis_performance/VAD_raw_scores_X_train.csv')
VAD_X_holdout <- read_csv('Data/lexicon_analysis_performance/VAD_raw_scores_X_holdout.csv')
VAD_y_train <- read_csv('Data/lexicon_analysis_performance/VAD_raw_scores_y_train.csv')
VAD_y_holdout <- read_csv('Data/lexicon_analysis_performance/VAD_raw_scores_y_holdout.csv')

VAD_train <- left_join(VAD_X_train, VAD_y_train)
VAD_holdout <- left_join(VAD_X_holdout, VAD_y_holdout)
```

Unpack predictions
```{r}
#for vad depression
VAD_depr_y_pred <- VAD_results$predicted_values[1] %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all(',,', ',') %>% 
  str_replace_all('[\n]', '')
VAD_depr_y_pred <- gsub('\\[', '', VAD_depr_y_pred)
VAD_depr_y_pred <- gsub('\\]', '', VAD_depr_y_pred)
VAD_depr_y_pred <- as.numeric(str_split(VAD_depr_y_pred, ',')[[1]])

#for vad anxiety
VAD_anx_y_pred <- VAD_results$predicted_values[2] %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all(',,', ',') %>% 
  str_replace_all('[\n]', '')
VAD_anx_y_pred <- gsub('\\[', '', VAD_anx_y_pred)
VAD_anx_y_pred <- gsub('\\]', '', VAD_anx_y_pred)
VAD_anx_y_pred <- as.numeric(str_split(VAD_anx_y_pred, ',')[[1]])

VAD_holdout <- VAD_holdout %>% 
  mutate(proportion_diff_depr_pred = VAD_depr_y_pred,
         proportion_diff_anx_pred = VAD_anx_y_pred)

```


Make plots
```{r}
VAD_holdout %>% 
  ggplot() + 
  aes(x=proportion_diff_depr_pred, y=proportion_diff_depr) +
  stat_smooth(method='lm') +
  geom_point() + 
  theme_minimal() 

VAD_holdout %>% 
  ggplot() + 
  aes(x=proportion_diff_anx_pred, y=proportion_diff_anx) +
  geom_point() + 
  stat_smooth(method='lm') +
  theme_minimal()
```

## Emotion
```{r}
emotion_results <- read_csv('Data/lexicon_analysis_performance/emotion_raw_scores_negposremoved.csv')
```

The we load the training and holdout datasets for plotting:
```{r}
emotion_X_train <- read_csv('Data/lexicon_analysis_performance/emotion_raw_scores_X_train.csv')
emotion_X_holdout <- read_csv('Data/lexicon_analysis_performance/emotion_raw_scores_X_holdout.csv')
emotion_y_train <- read_csv('Data/lexicon_analysis_performance/emotion_raw_scores_y_train.csv')
emotion_y_holdout <- read_csv('Data/lexicon_analysis_performance/emotion_raw_scores_y_holdout.csv')

emotion_train <- left_join(emotion_X_train, emotion_y_train)
emotion_holdout <- left_join(emotion_X_holdout, emotion_y_holdout)
```

Unpack predictions
```{r}
#for emotion depression
emotion_depr_y_pred <- emotion_results$predicted_values[1] %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all('[\n]', '')
emotion_depr_y_pred <- gsub('\\[,', '', emotion_depr_y_pred)
emotion_depr_y_pred <- gsub('\\[', '', emotion_depr_y_pred)
emotion_depr_y_pred <- gsub('\\,]', '', emotion_depr_y_pred)
emotion_depr_y_pred <- as.numeric(str_split(emotion_depr_y_pred, ',')[[1]])

#for emotion anxiety
emotion_anx_y_pred <- emotion_results$predicted_values[2] %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all('[\n]', '')
emotion_anx_y_pred <- gsub('\\[,', '', emotion_anx_y_pred)
emotion_anx_y_pred <- gsub('\\,]', '', emotion_anx_y_pred)
emotion_anx_y_pred <- as.numeric(str_split(emotion_anx_y_pred, ',')[[1]])

emotion_holdout <- emotion_holdout %>% 
  mutate(proportion_diff_depr_pred = emotion_depr_y_pred,
         proportion_diff_anx_pred = emotion_anx_y_pred)

```


Make plots
```{r}
emotion_holdout %>% 
  ggplot() + 
  aes(x=proportion_diff_depr_pred, y=proportion_diff_depr) +
  geom_point() + 
  theme_minimal() 

emotion_holdout %>% 
  ggplot() + 
  aes(x=proportion_diff_anx_pred, y=proportion_diff_anx) +
  geom_point() + 
  theme_minimal()
```

## Checking colinearity
```{r}
#compute correlation matrix
word_diff_emotion <- word_diff_emotion %>% mutate_at(c(5:14), as.numeric)

corr <- round(cor(word_diff_emotion[c('anticipation','sadness','disgust')]), 2)

# Compute a matrix of correlation p-values
#p_values <- cor_pmat(word_diff_emotion[6:15])

ggcorrplot(corr,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           colors = c("#6D9EC1", "white", "#E46726"),
           lab = TRUE)


#make the partial correlation matrix for depression
hep <- round(partial.r(data = word_diff_emotion,
                 x = c('anticipation','sadness','disgust'),
                 y = 4, 
                 method = 'kendall'
                 )
             ,2)

#making the correlation plot
plot_depr <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           colors = c("#6D9EC1", "white", "#E46726")) + labs(title = 'Partial Correlation of emotion lexicon with target Depression')
           
#make the partial correlation matrix for anxiety
hep <- round(partial.r(data = word_diff_emotion,
                 x = c('anticipation','sadness','disgust'),
                 y = 5, 
                 method = 'kendall'
                 )
             ,2)

#making the correlation plot
plot_anx <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           colors = c("#6D9EC1", "white", "#E46726")) + labs(title = 'Partial Correlation of emotion lexicon with target Anxiety')
           
plot_depr

plot_anx

```

## Feature Importance

We manually make a dataframe for Depression and anxiety
```{r}
depr_feature_importance <- tibble(
  'feature_name' = c('Valence', 'Fear'),
  'feature_importance_train' = c(0.149, 0.0814),
  'feature_importance_holdout' = c(0.177, 0.0801),
  'std_train' = c(0.0322, 0.028),
  'std_holdout' = c(0.0405, 0.0281),
  'direction' = c('positive', 'negative')
)

anx_feature_importance <- tibble(
  'feature_name' = c('Valence', 'Anticipation', 'Disgust', 'Sadness'),
  'feature_importance_train' = c(0.102, 0.0203, 0.0700, 0.0504),
  'feature_importance_holdout' = c(0.144, -0.0301, 0.0600, 0.0519),
  'std_train' = c(0.0274, 0.0117, 0.0212, 0.0202),
  'std_holdout' = c(0.0319, 0.0128, 0.0250, 0.0222),
  'direction' = c('positive', 'negative', 'negative', 'negative')
)
```

## Plots

```{r}
depr_train <- depr_feature_importance %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_importance_train), y = feature_importance_train) +
  geom_bar(aes(fill = direction), stat = 'identity', width = 0.5) +
  geom_errorbar(aes(ymin=feature_importance_train-std_train, ymax=feature_importance_train+std_train), width=.15) +
  scale_fill_manual(values = color_palette) +
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Feature Importance (R2)') +
  theme(axis.text.x = element_text(angle = 30,size=24,vjust=0.5), axis.title.y=element_text(size=24), axis.text.y = element_text(size=18)) + 
  #geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE) + 
  scale_y_continuous(breaks = c(-0.05, 0.00, 0.05, 0.10, 0.15, 0.20),
                     limits = c(0, 0.22))

depr_holdout <- depr_feature_importance %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_importance_holdout), y = feature_importance_holdout) +
  geom_bar(aes(fill = direction), stat = 'identity', width = 0.5) +
  geom_errorbar(aes(ymin=feature_importance_holdout-std_holdout, ymax=feature_importance_holdout+std_holdout), width=.15) +
  scale_fill_manual(values = color_palette) + 
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Feature Importance (R2)') +
  theme(axis.text.x = element_text(angle = 30,size=24,vjust=0.5), axis.title.y=element_text(size=24), axis.text.y = element_text(size=18)) +  
  #geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE) +
  scale_y_continuous(breaks = c(-0.05, 0.00, 0.05, 0.10, 0.15, 0.20),
                     limits = c(0, 0.22))# +
  #theme(axis.title.y=element_blank(),
  #      axis.text.y=element_blank(),
  #      axis.ticks.y=element_blank())

anx_train <-anx_feature_importance %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_importance_train), y = feature_importance_train) +
  geom_bar(aes(fill = direction), stat = 'identity') +
  geom_errorbar(aes(ymin=feature_importance_train-std_train, ymax=feature_importance_train+std_train), width=.15,
                 position=position_dodge(.9)) +
  scale_fill_manual(values = color_palette) +
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Feature Importance (R2)') +
  theme(axis.text.x = element_text(angle = 30,size=24,vjust=0.5), axis.title.y=element_text(size=24), axis.text.y = element_text(size=18)) +  
  #geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE) + 
  scale_y_continuous(breaks = c(-0.05, 0.00, 0.05, 0.10, 0.15, 0.20),
                     limits = c(-0.05, 0.22))

anx_holdout <-anx_feature_importance %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_importance_holdout), y = feature_importance_holdout) + 
  geom_bar(aes(fill = direction), stat = 'identity') +
  geom_errorbar(aes(ymin=feature_importance_holdout-std_holdout, ymax=feature_importance_holdout+std_holdout), width=.15,
                 position=position_dodge(.9)) +
  scale_fill_manual(values = color_palette) +
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Feature Importance (R2)') +
  theme(axis.text.x = element_text(angle = 30,size=24,vjust=0.5), axis.title.y=element_text(size=24), axis.text.y = element_text(size=18)) + 
  #geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE) +
  scale_y_continuous(breaks = c(-0.05, 0.00, 0.05, 0.10, 0.15, 0.20),
                     limits = c(-0.05, 0.22))# +
  #theme(axis.title.y=element_blank(),
  #      axis.text.y=element_blank(),
  #      axis.ticks.y=element_blank())

#png('figures/lexicon_analysis/feature_importance_depr.png', width = 15, height = 10, units = 'in', res = 300)
#depr_train + depr_holdout  + plot_annotation(
#  title = 'a) Depression',
#  subtitle = '') & theme(plot.title = element_text(size = 18))
#dev.off()

#png('figures/lexicon_analysis/feature_importance_anx.png', width = 15, height = 10, units = 'in', res = 300)
#anx_train + anx_holdout  + plot_annotation(
#  title = 'b) Anxiety',
#  subtitle = '') & theme(plot.title = element_text(size = 18))
#dev.off()


png('figures/lexicon_analysis/feature_importance_depr_train.png', width = 10, height = 10, units = 'in', res = 300)
depr_train
dev.off()

png('figures/lexicon_analysis/feature_importance_depr_holdout.png', width = 10, height = 10, units = 'in', res = 300)
depr_holdout
dev.off()

png('figures/lexicon_analysis/feature_importance_anx_train.png', width = 10, height = 10, units = 'in', res = 300)
anx_train
dev.off()

png('figures/lexicon_analysis/feature_importance_anx_holdout.png', width = 10, height = 10, units = 'in', res = 300)
anx_holdout
dev.off()
```



## General table
```{r, eval = F}

models_emotion <- tibble(
  var_name_1 = character(),
  var_name_2 = character(),
  var_name_3 = numeric(),
)

for (outcome in colnames(word_diff_emotion)[c(2,13)]){
  
  for (predictor in list(colnames(word_diff_emotion)[3:12])) {
    
    #predictor = as.factor(predictor)
    #outcome = as.factor(outcome)
    
    model <- lm(paste('proportion_diff_depr',  '~', predictor), data = word_diff_emotion)
    output <- c(summary(model)$r.squared)
    models_emotion <- rbind(outcome, 'proportion_diff_depr', output)
  }
}

for(i in 2:ncol(data)) {                 # Head of for-loop
 
  predictors_i <- colnames(data)[2:i]    # Create vector of predictor names
  mod_summaries[[i - 1]] <- summary(     # Store regression model summary in list
    lm(y ~ ., data[ , c("y", predictors_i)]))
 
}

summary(ea10)$coefficients
summary(ea10)$r.squared
summary(ea10)$adj.r.squared


word_anx_diff <- tibble()

i = 1
for (row in seq(1, by=2, len=length(unique(te$Word)))) {
    diff = word_anx_proportion$Proportion[row]-word_anx_proportion$Proportion[row+1] 
    output = c(as.character(word_anx_proportion$Word[row]), diff)
    word_anx_diff <- rbind(word_anx_diff, output)
    i = i + 1
}


```






