---
title: "words_as_predictors_new_plots"
author: "Anders Hjulmand"
date: "2022-10-04"
output: html_document
---

We load Libraries
```{r}
pacman::p_load(tidyverse, wesanderson, patchwork, ggcorrplot, tidytext, kableExtra, see, correlation, psych, ggridges, sjmisc, mctest, grid)
```

We define a color palette for plots
```{r}
color_palette <- c(wes_palette("Darjeeling1")[2], wes_palette("Darjeeling1")[3])
```


# Preprocessing 

We load the data into its raw format.
```{r}
data_raw <- read.csv("Data/ThisThat_Prolific2_2019_04_01_txt.csv", sep = ',', header = T,skip=1)
```

And do some wrangling.
```{r}
data <- data_raw

data <- data %>% 
  slice(-1) %>% 
  filter(Finished == 'True') %>% 
  select(6,9,14,15,17,19:ncol(data)) %>% 
  rename('Duration' = 'Duration..in.seconds.',
         'ID' = 'Response.ID',
         'Latitude' = 'Location.Latitude',
         'Longitude' = 'Location.Longitude',
         'Language' = 'User.Language',
         'Gender' = 'Please.indicate.your.gender',
         'Age' = 'Please.indicate.your.age',
         'Native_English' = 'Is.your.native.language.English.',
         'Native_Language' = 'What.is.your.native.language.',
         'Variety_English' = 'Which.variety.of.English.is.your.native.language....Selected.Choice',
         'Variety_English_Other' = 'Which.variety.of.English.is.your.native.language....Other..please.type.in.....Text') %>% 
  mutate_at(c('ID', 'Language', 'Gender', 'Age', 'Native_English', 'Native_Language', 'Variety_English', 'Variety_English_Other'), factor)
      


#For some reason the word "banjo" has snug in here and there
colnames(data)[c(42,273,189,210,249,270,309,330,369,390,429,450)]<- c('mushroom','hierarchy','bay','hall','arm','ham','banana','engineer','ant','handshake','axe','gratitude')

#Create a factor variable for the different groups and add it as a column to the data
wordGroup<-as.factor(rowSums(matrix(c(1*(data$helped!=''),2*(data$aggressive!=''),3*(data$activist!=''),4*(data$accordion!=''),5*(data$damaged!=''),6*(data$alligator!=''),7*(data$accident!=''),8*(data$actor!='')),ncol=8)))
data <- data %>% 
  mutate(Group = as.factor(wordGroup))

#drop levels
data<-droplevels(data)

#selecting only words and groupnumber and ID as column.
data <- data %>% 
  select(c('Group', 'ID', 6:485)) %>% 
  mutate(across(c(3:482), ~recode(., 'this' = '-1'))) %>% 
  mutate(across(c(3:482), ~recode(., 'that' = '1'))) 

```

Making list of dataframes for each group, where we only keep the words in the group and merge with the factor scores from the 2-factor analysis.
```{r}
#loading the scores from factor analysis
targets <- read_csv('Data/target.csv')
targets <- targets %>%  mutate(ID = as.factor(ID))

datasets <- group_split(data, with(data, Group), keep = FALSE) %>% as.list()

i = 1
for (dataset in datasets){
  datasets[[i]] <- datasets[[i]] %>% 
  select(-c(Group)) %>% 
  discard(~all(is.na(.) | . =="")) %>% 
  mutate_at(c(2:61), as.numeric)
  datasets[[i]] <- left_join(datasets[[i]],
                             targets,
                             by = 'ID')
  i = i + 1
  
}
```

Saving each dataframe by itself.
```{r}
i = 1
for (i in seq_along(datasets)) {
    filename = paste0('Data/words_as_predictors/group_',i,".csv")
    write_csv(datasets[[i]], filename)
    i = i + 1
}
```


# Python code

------------------------Python code------------------------
running python code from script words_as_predictors.ipynb
-----------------------------------------------------------

# Plotting Results

Load data from python script and do some cleaning
```{r}
df <- read_csv("Data/words_as_predictors_performance/jatjak2.csv") %>% 
  mutate(group = case_when(group == 1 ~ 'Group 1',
                           group == 2 ~ 'Group 2',
                           group == 3 ~ 'Group 3',
                           group == 4 ~ 'Group 4',
                           group == 5 ~ 'Group 5',
                           group == 6 ~ 'Group 6',
                           group == 7 ~ 'Group 7',
                           group == 8 ~ 'Group 8'),
         target = case_when(target == 'Depressed_F1' ~ 'Depression',
                            target == 'Anxiety_F2' ~ 'Anxiety')) %>% 
  select(-1)
```

## Train and Holdout sets Mean and Mode

First we load all the train and holdout datasets. Then we find the proportion of patients in each group for train and holdout.

Defining a function to find mode
```{r}
find_mode <- function(x) {
  u <- unique(x)
  tab <- tabulate(match(x, u))
  u[tab == max(tab)]
}
```

```{r, message = F}
files <- list.files('Data/words_as_predictors_train_holdout/')

train_holdout <- tibble(i = numeric(),
                        group = factor(),
                        type = factor(),
                        proportion_depr = numeric(),
                        proportion_anx = numeric())
i=1
for (dataset_name in files){
  #reading the dataset
  dataset = read_csv(paste0('Data/words_as_predictors_train_holdout/', dataset_name))

#saving information
group = as.numeric(str_extract(dataset_name, "(\\d)+"))
type = str_sub(dataset_name, 3, 7)
proportion_depr = 1-(sum(dataset$Depressed_F1)/nrow(dataset))
proportion_anx = 1-(sum(dataset$Anxiety_F2)/nrow(dataset))

output = c(i, group, type, proportion_depr, proportion_anx)
train_holdout <- rbind(train_holdout, output)
  
i=i+1

}
train_holdout <- train_holdout %>% 
  rename(
    'i' = 1,
    'group' = 2,
    'type' = 3,
    'proportion_depr' = 4,
    'proportion_anx' = 5
  )
```


## Ridgeplot Permutation Test 1

Here we make stacked density plots for permutation test 1.


### Holdout
```{r}
perm_scores <- tibble()

for (i in seq(1,nrow(df), 1)){
#wrangling permutation scores to values  
perm_score <- df$permutation_scores_holdout[i] %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all('[\n]', '') %>% 
  str_replace_all('[\"]', '')
perm_score <- as.numeric(str_split(perm_score, ',')[[1]])
perm_score <- perm_score[!is.na(perm_score)]

#logging information
group <- df$group[i]
target <- df$target[i]
best_model_name <- df$best_model_name[i]
best_model_train_score = df$best_model_train_accuracy[i]
best_model_holdout_score <- df$best_model_holdout_accuracy[i]
permutation_accuracy_train = df$permutation_accuracy_train[i]
permutation_accuracy_holdout = df$permutation_accuracy_holdout[i]
permutation_pvalue_train <- df$permutation_pvalue_train[i]
permutation_pvalue_holdout = df$permutation_pvalue_holdout[i]

#manually calculating p-value from permutation test
percentile = ecdf(perm_score)
permutation_pvalue_holdout_manual = 1-(percentile(best_model_holdout_score))
permutation_mean_holdout = mean(perm_score)
permutation_mode_holdout = find_mode(perm_score)

#saving output
output = c(group, target, best_model_name, best_model_train_score, best_model_holdout_score, permutation_accuracy_train, permutation_accuracy_holdout, permutation_pvalue_train, permutation_pvalue_holdout, permutation_pvalue_holdout_manual, permutation_mean_holdout, permutation_mode_holdout, perm_score)

perm_scores <- rbind(perm_scores, output)

}

perm_scores <- perm_scores %>% 
  rename('group_nr' = 1,
         'target' = 2,
         'best_model_name' = 3,
         'best_model_train_score' = 4,
         'best_model_holdout_score' = 5,
         'permutation_accuracy_train' = 6,
         'permutaion_accuracy_holdout' = 7,
         'permutation_pvalue_train' = 8,
         'permutation_pvalue_holdout' = 9,
         'permutation_pvalue_holdout_manual' = 10,
         'permutation_mean_holdout' = 11,
         'permutation_mode_holdout' = 12)

#Adding the manually calculated p-value to the raw dataset
df <- df %>% mutate(permutation_pvalue_holdout_manual = perm_scores$permutation_pvalue_holdout_manual,
                    permutation_mean_holdout = perm_scores$permutation_mean_holdout,
                    permutation_mode_holdout = perm_scores$permutation_mode_holdout)

```

```{r}
depr_holdout <- perm_scores %>% 
  filter(target == 'Depression') %>% 
  gather(c(12:length(perm_scores)),
         key = permutation_group,
         value = value) %>% 
  ggplot() + 
  aes(x=as.numeric(value), y=factor(group_nr), group = factor(group_nr)) +  
  geom_density_ridges(fill = wes_palette("Zissou1")[2], scale = 1) + 
  theme_minimal() + 
  labs(x='Accuracy score', y = 'Group') + 
  scale_x_continuous(breaks = c(0.50, 0.55, 0.60, 0.65, 0.70, 0.75, 0.80),
                     limits = c(0.50, 0.80)) +
  theme(axis.title.y = element_blank(), axis.text.y = element_text(size=14), axis.text.x = element_text(size=14), axis.title.x = element_text(size=14))

anx_holdout <- perm_scores %>% 
  filter(target == 'Anxiety') %>% 
  gather(c(12:length(perm_scores)),
         key = permutation_group,
         value = value) %>% 
  ggplot() + 
  aes(x=as.numeric(value), y=factor(group_nr), group = factor(group_nr)) +  
  geom_density_ridges(fill = wes_palette("Zissou1")[2], scale = 1) + 
  theme_minimal() + 
  labs(x='Accuracy score', y = 'Group') + 
  scale_x_continuous(breaks = c(0.50, 0.55, 0.60, 0.65, 0.70, 0.75, 0.80),
                     limits = c(0.50, 0.80)) +
  theme(axis.title.y = element_blank(), axis.text.y = element_text(size=14), axis.text.x = element_text(size=14), axis.title.x = element_text(size=14))

#png('figures/words_as_predictors/permutation_holdout_depr.PNG', width = 10, height = 12, units = 'in', res = 300)
depr_holdout
dev.off()

#png('figures/words_as_predictors/permutation_holdout_anx.PNG', width = 10, height = 12, units = 'in', res = 300)
anx_holdout
dev.off()
```

### Train

```{r}
perm_scores <- tibble()

for (i in seq(1,nrow(df), 1)){
#wrangling permutation scores to values  
perm_score <- df$permutation_scores_train[i] %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all('[\n]', '') %>% 
  str_replace_all('[\"]', '')
perm_score <- as.numeric(str_split(perm_score, ',')[[1]])
perm_score <- perm_score[!is.na(perm_score)]

#logging information
group <- df$group[i]
target <- df$target[i]
best_model_name <- df$best_model_name[i]
best_model_train_score = df$best_model_train_accuracy_cv[i]
best_model_holdout_score <- df$best_model_holdout_accuracy[i]
permutation_accuracy_train = df$permutation_accuracy_train[i]
permutation_accuracy_holdout = df$permutation_accuracy_holdout[i]
permutation_pvalue_train <- df$permutation_pvalue_train[i]
permutation_pvalue_holdout = df$permutation_pvalue_holdout[i]

#manually calculating p-value from permutation test
percentile = ecdf(perm_score)
permutation_pvalue_train_manual = 1-(percentile(best_model_train_score))
permutation_mean_train = mean(perm_score)
permutation_mode_train = find_mode(perm_score)

#saving output
output = c(group, target, best_model_name, best_model_train_score, best_model_holdout_score, permutation_accuracy_train, permutation_accuracy_holdout, permutation_pvalue_train, permutation_pvalue_holdout, permutation_pvalue_train_manual, permutation_mean_train, permutation_mode_train, perm_score)

perm_scores <- rbind(perm_scores, output)

}

perm_scores <- perm_scores %>% 
  rename('group_nr' = 1,
         'target' = 2,
         'best_model_name' = 3,
         'best_model_train_score' = 4,
         'best_model_holdout_score' = 5,
         'permutation_accuracy_train' = 6,
         'permutaion_accuracy_holdout' = 7,
         'permutation_pvalue_train' = 8,
         'permutation_pvalue_holdout' = 9,
         'permutation_pvalue_train_manual' = 10,
         'permutation_mean_train' = 11,
         'permutation_mode_train' = 12)

#Adding the manually calculated p-value to the raw dataset
df <- df %>% mutate(permutation_pvalue_train_manual = perm_scores$permutation_pvalue_train_manual,
                    permutation_mean_train = perm_scores$permutation_mean_train,
                    permutation_mode_train = perm_scores$permutation_mode_train)

```

```{r}
depr_holdout <- perm_scores %>% 
  filter(target == 'Depression') %>% 
  gather(c(12:length(perm_scores)),
         key = permutation_group,
         value = value) %>% 
  ggplot() + 
  aes(x=as.numeric(value), y=factor(group_nr), group = factor(group_nr)) +  
  geom_density_ridges(fill = wes_palette("Zissou1")[2], scale = 1) + 
  theme_minimal() + 
  labs(x='Accuracy score', y = 'Group') + 
  scale_x_continuous(breaks = c(0.50, 0.55, 0.60, 0.65, 0.70, 0.75, 0.80),
                     limits = c(0.60, 0.80)) +
  theme(axis.title.y = element_blank(), axis.text.y = element_text(size=14), axis.text.x = element_text(size=14), axis.title.x = element_text(size=14))

anx_holdout <- perm_scores %>% 
  filter(target == 'Anxiety') %>% 
  gather(c(12:length(perm_scores)),
         key = permutation_group,
         value = value) %>% 
  ggplot() + 
  aes(x=as.numeric(value), y=factor(group_nr), group = factor(group_nr)) +  
  geom_density_ridges(fill = wes_palette("Zissou1")[2], scale = 1) + 
  theme_minimal() + 
  labs(x='Accuracy score', y = 'Group') + 
  scale_x_continuous(breaks = c(0.50, 0.55, 0.60, 0.65, 0.70, 0.75, 0.80),
                     limits = c(0.60, 0.80)) +
  theme(axis.title.y = element_blank(), axis.text.y = element_text(size=14), axis.text.x = element_text(size=14), axis.title.x = element_text(size=14))

png('figures/words_as_predictors/permutation_train_depr.PNG', width = 10, height = 12, units = 'in', res = 300)
depr_holdout
dev.off()

png('figures/words_as_predictors/permutation_train_anx.PNG', width = 10, height = 12, units = 'in', res = 300)
anx_holdout
dev.off()



```


## Feature Plots

We first make a dataframe with one row for each feature and tons of information.
```{r}
features_df <- tibble()

for (i in seq(1,nrow(df), 1)){
  print(i)
  
  #setting up dataframes
  feature_df_small <- tibble(feature_name = character(),
                             coefficient = numeric())
  
  feature_names_df <- tibble()
  feature_importances_train_df <- tibble()
  feature_std_train_df <- tibble()
  feature_importances_holdout_df <- tibble()
  feature_std_holdout_df <- tibble()
  feature_coefs_df <- tibble()
  
#adding some information
group = df$group[i]
target = df$target[i]
train_accuracy = df$best_model_train_accuracy_cv[i]
holdout_accuracy = df$best_model_holdout_accuracy[i]
permutation_pvalue_train_manual = df$permutation_pvalue_train_manual[i]
permutation_pvalue_holdout_manual = df$permutation_pvalue_holdout_manual[i]

#looping over feature names
feature_names <- df$feature_names[i] %>% 
  str_replace_all('[\"]', '') %>% 
  str_replace_all('[\']', '') %>% 
  str_replace_all('[(]|[)]', '') %>% 
  str_replace_all(' ', '')
feature_names <- str_split(feature_names, ',')[[1]]
feature_names_df <- rbind(feature_names_df, feature_names) %>% rotate_df()
print('name')

#looping over importances and cleaning them TRAIN
importances_train <- df$FI_mean_train[i] %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all(',,,,', ',') %>% 
  str_replace_all(',,,', ',') %>% 
  str_replace_all(',,', ',') %>% 
  str_replace_all('[\n]', '')
importances_train <- gsub('\\[,', '', importances_train)
importances_train <- gsub('\\[\\[', '', importances_train)
importances_train <- gsub('\\,]', '', importances_train)
importances_train <- gsub('\\[', '', importances_train)
importances_train <- gsub('\\]', '', importances_train)
importances_train <- as.numeric(str_split(importances_train, ',')[[1]])
feature_importances_train_df <- rbind(feature_importances_train_df, importances_train) %>% rotate_df()
print('coef')

#looping over standard deviations for importances TRAIN
stds_train <- df$FI_std_train[i]  %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all(',,,,', ',') %>% 
  str_replace_all(',,,', ',') %>% 
  str_replace_all(',,', ',') %>% 
  str_replace_all('[\n]', '')
stds_train <- gsub('\\[,', '', stds_train)
stds_train <- gsub('\\[\\[', '', stds_train)
stds_train <- gsub('\\,]', '', stds_train)
stds_train <- gsub('\\[', '', stds_train)
stds_train <- gsub('\\]', '', stds_train)
stds_train <- as.numeric(str_split(stds_train, ',')[[1]])
feature_std_train_df <- rbind(feature_std_train_df, stds_train) %>% rotate_df()

#looping over importances and cleaning them HOLDOUT
importances_holdout <- df$FI_mean_holdout[i] %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all(',,,,', ',') %>% 
  str_replace_all(',,,', ',') %>% 
  str_replace_all(',,', ',') %>% 
  str_replace_all('[\n]', '')
importances_holdout <- gsub('\\[,', '', importances_holdout)
importances_holdout <- gsub('\\[\\[', '', importances_holdout)
importances_holdout <- gsub('\\,]', '', importances_holdout)
importances_holdout <- gsub('\\[', '', importances_holdout)
importances_holdout <- gsub('\\]', '', importances_holdout)
importances_holdout <- as.numeric(str_split(importances_holdout, ',')[[1]])
feature_importances_holdout_df <- rbind(feature_importances_holdout_df, importances_holdout) %>% rotate_df()
print('coef')

#looping over standard deviations for importances HOLDOUT
stds_holdout <- df$FI_std_holdout[i]  %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all(',,,,', ',') %>% 
  str_replace_all(',,,', ',') %>% 
  str_replace_all(',,', ',') %>% 
  str_replace_all('[\n]', '')
stds_holdout <- gsub('\\[,', '', stds_holdout)
stds_holdout <- gsub('\\[\\[', '', stds_holdout)
stds_holdout <- gsub('\\,]', '', stds_holdout)
stds_holdout <- gsub('\\[', '', stds_holdout)
stds_holdout <- gsub('\\]', '', stds_holdout)
stds_holdout <- as.numeric(str_split(stds_holdout, ',')[[1]])
feature_std_holdout_df <- rbind(feature_std_holdout_df, stds_holdout) %>% rotate_df()


#looping over coefficients and cleaning them
coefs <- df$best_model_coef[i] %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all(' ', ',') %>% 
  str_replace_all(',,,,', ',') %>% 
  str_replace_all(',,,', ',') %>% 
  str_replace_all(',,', ',') %>% 
  str_replace_all('[\n]', '')
coefs <- gsub('\\[\\[,', '', coefs)
coefs <- gsub('\\[\\[', '', coefs)
coefs <- gsub('\\]\\]|\\,]\\]', '', coefs)
coefs <- as.numeric(str_split(coefs, ',')[[1]])
feature_coefs_df <- rbind(feature_coefs_df, coefs) %>% rotate_df()
print('coef')

output = cbind(i, group, target, train_accuracy, holdout_accuracy, permutation_pvalue_train_manual, permutation_pvalue_holdout_manual, feature_names_df, feature_importances_train_df, feature_std_train_df, feature_importances_holdout_df, feature_std_holdout_df, feature_coefs_df)
print('output')
features_df <- rbind(features_df, output)
print('large_df')
}

features_df <- features_df %>% 
  rename('feature_name' = 8,
         'feature_importance_train' = 9,
         'feature_importance_std_train' = 10,
         'faeture_importance_holdout' = 11,
         'feature_importance_std_holdout' = 12,
         'feature_coefficient' = 13) %>% 
   mutate('feature_coefficient_odds_ratio' = exp(feature_coefficient),
          direction = ifelse(feature_coefficient < 0, 'negative', 'positive'),
          direction = as.factor(direction))
```

## Coefficient Plots

We make plots for beta coefficients for each word.
```{r}
depr_train <- features_df %>% 
  filter(target=='Depression') %>% 
  filter(permutation_pvalue_train_manual < 0.05) %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_coefficient), y = feature_coefficient) + geom_bar(aes(fill = feature_coefficient), stat = 'identity') +
  scale_fill_distiller(palette = 'RdYlGn',direction = 1) + 
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Coefficients', title = 'Training Dataset') +
  theme(axis.text.x = element_text(angle = 90,size=12,hjust=1),axis.title.y=element_text(size=16)) +
  geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE)

depr_holdout <- features_df %>% 
  filter(target=='Depression') %>% 
  filter(permutation_pvalue_holdout_manual < 0.05) %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_coefficient), y = feature_coefficient) + geom_bar(aes(fill = feature_coefficient), stat = 'identity') +
  scale_fill_distiller(palette = 'RdYlGn',direction = 1) + 
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Coefficients', title = 'Holdout Dataset') +
  theme(axis.text.x = element_text(angle = 90,size=12,hjust=1),axis.title.y=element_text(size=16)) +
  geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE)

depr_train + depr_holdout  + plot_annotation(
  title = 'Coefficients of Words in Significant Models predicting Depression',
  subtitle = '')

anx_train_1 <- features_df %>% 
  filter(target=='Anxiety') %>% 
  filter(permutation_pvalue_train_manual < 0.05) %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_coefficient), y = feature_coefficient) + geom_bar(aes(fill = feature_coefficient), stat = 'identity') +
  scale_fill_distiller(palette = 'RdYlGn',direction = 1) + 
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Coefficients', title = 'Training Dataset') +
  theme(axis.text.x = element_text(angle = 90,size=12,hjust=1),axis.title.y=element_text(size=16)) +
  geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE)

anx_train <- features_df %>% 
  filter(target=='Anxiety') %>% 
  filter(permutation_pvalue_train_manual < 0.05) %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_coefficient), y = feature_coefficient) + geom_bar(aes(fill = feature_coefficient), stat = 'identity') +
  scale_fill_distiller(palette = 'RdYlGn',direction = 1) + 
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Coefficients', title = 'Training Dataset') +
  theme(axis.text.x = element_text(angle = 90,size=12,hjust=1),axis.title.y=element_text(size=16)) +
  geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE)

anx_holdout <- features_df %>% 
  filter(target=='Anxiety') %>% 
  filter(permutation_pvalue_holdout_manual < 0.05) %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_coefficient), y = feature_coefficient) + geom_bar(aes(fill = feature_coefficient), stat = 'identity') +
  scale_fill_distiller(palette = 'RdYlGn',direction = 1) + 
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Coefficients', title = 'Holdout Dataset') +
  theme(axis.text.x = element_text(angle = 90,size=12,hjust=1),axis.title.y=element_text(size=16)) +
  geom_text(mapping = aes(x = Inf, y = -Inf, label = 'blablabla'),hjust=1, vjust=-1,inherit.aes = FALSE)

anx_train + anx_holdout  + plot_annotation(
  title = 'Coefficients of Words in Significant Models predicting Anxiety',
  subtitle = '')
```


## Feature Importance Plots

We make plots for feature importance of words.
```{r}
depr_train <- features_df %>% 
  filter(target=='Depression') %>% 
  filter(permutation_pvalue_train_manual < 0.05) %>% 
  filter(feature_importance_train != 0) %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_importance_train), y = feature_importance_train) +
  geom_bar(aes(fill = direction), stat = 'identity') +
  geom_errorbar(aes(ymin=feature_importance_train-feature_importance_std_train, ymax=feature_importance_train+feature_importance_std_train), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_manual(values = color_palette) + 
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Feature Importance (Accuracy)', title = '') +
  theme(axis.text.y = element_text(size=8,hjust=1),axis.title.y=element_text(size=14)) +
  geom_text(mapping = aes(x = Inf, y = -Inf, label = 'p(permutation) < 0.01'),hjust=1, vjust=-1,inherit.aes = FALSE) + 
  coord_flip() + 
  annotation_custom(grobTree(textGrob("p(permutation) < 0.01", x=0.8,  y=0.05, hjust=0,
  gp=gpar(col="darkslateblue", fontsize=12, fontface="italic"))))

  depr_holdout <- features_df %>% 
  filter(target=='Depression') %>% 
  filter(permutation_pvalue_holdout_manual < 0.05) %>% 
  filter(faeture_importance_holdout != 0) %>% 
  ggplot() +
  aes(x = reorder(feature_name, faeture_importance_holdout), y = faeture_importance_holdout) +
  geom_bar(aes(fill = direction), stat = 'identity') +
  geom_errorbar(aes(ymin=faeture_importance_holdout-feature_importance_std_holdout, ymax=faeture_importance_holdout+feature_importance_std_holdout), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_manual(values = color_palette) +  
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Feature Importance (Accuracy)', title = '') +
  theme(axis.text.y = element_text(size=12,hjust=1),axis.title.y=element_text(size=14)) +
  #geom_text(mapping = aes(x = Inf, y = -Inf, label = 'p(permutation < 0.05'),hjust=1, vjust=-1,inherit.aes = FALSE)  + 
  coord_flip() + 
  annotation_custom(grobTree(textGrob("p(permutation) < 0.05", x=0.8,  y=0.05, hjust=0,
  gp=gpar(col="darkslateblue", fontsize=12, fontface="italic"))))

#depr_train + depr_holdout  + plot_annotation(
#  title = 'Feature Importance of Words in Significant Models predicting Depression',
#  subtitle = '')

anx_train <- features_df %>% 
  filter(target=='Anxiety') %>% 
  filter(permutation_pvalue_train_manual < 0.05) %>% 
  filter(feature_importance_train != 0) %>% 
  ggplot() +
  aes(x = reorder(feature_name, feature_importance_train), y = feature_importance_train) +
  geom_bar(aes(fill = direction), stat = 'identity') +
  geom_errorbar(aes(ymin=feature_importance_train-feature_importance_std_train, ymax=feature_importance_train+feature_importance_std_train), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_manual(values = color_palette) +  
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Feature Importance (Accuracy)', title = '') +
  theme(axis.text.y = element_text(size=7.5,hjust=1),axis.title.y=element_text(size=14)) +
  #geom_text(mapping = aes(x = Inf, y = -Inf, label = 'p(permutation) < 0.01'),hjust=1, vjust=-1,inherit.aes = FALSE) + 
  coord_flip() + 
  annotation_custom(grobTree(textGrob("p(permutation) < 0.01", x=0.8,  y=0.05, hjust=0,
  gp=gpar(col="darkslateblue", fontsize=12, fontface="italic")))) 

anx_holdout <- features_df %>% 
  filter(target=='Anxiety') %>% 
  filter(permutation_pvalue_holdout_manual < 0.05) %>% 
  filter(faeture_importance_holdout != 0) %>% 
  ggplot() +
  aes(x = reorder(feature_name, faeture_importance_holdout), y = faeture_importance_holdout) +
  geom_bar(aes(fill = direction), stat = 'identity') +
  geom_errorbar(aes(ymin=faeture_importance_holdout-feature_importance_std_holdout, ymax=faeture_importance_holdout+feature_importance_std_holdout), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_manual(values = color_palette) + 
  theme_minimal() + 
  theme(legend.position='none') +
  labs(x='', y = 'Feature Importance (Accuracy)', title = '') +
  theme(axis.text.y = element_text(size=12,hjust=1),axis.title.y=element_text(size=14)) +
  #geom_text(mapping = aes(x = Inf, y = -Inf, label = 'p(permutation) < 0.05'),hjust=1, vjust=-1,inherit.aes = FALSE) + 
  coord_flip() + 
  annotation_custom(grobTree(textGrob("p(permutation) < 0.05", x=0.8,  y=0.05, hjust=0,
  gp=gpar(col="darkslateblue", fontsize=12, fontface="italic"))))

#anx_train + anx_holdout  + plot_annotation(
#  title = 'Feature Importance of Words in Significant Models predicting Anxiety',
#  subtitle = '')

png('figures/words_as_predictors/permutation_importance_deprtrain.png', width = 10, height = 12, units = 'in', res = 300)
depr_train
dev.off()

png('figures/words_as_predictors/permutation_importance_deprholdout.png', width = 10, height = 8, units = 'in', res = 300)
depr_holdout
dev.off()

png('figures/words_as_predictors/permutation_importance_anxtrain.png', width = 10, height = 17, units = 'in', res = 300)
anx_train
dev.off()

png('figures/words_as_predictors/permutation_importance_anxholdout.png', width = 10, height = 10, units = 'in', res = 300)
anx_holdout
dev.off()

```


## Plotting pairwise partial correlation of features

We can also make a partial correlation matrix for each target in each group.
```{r}
best_features = as.character((df %>% filter(group == 'Group 1') %>%
                                filter(target ==  'Depressed') %>%
                                select(feature_names)))
best_features = str_replace_all(best_features, '[[:punct:]]', "")
best_features = str_split(best_features, " ")
best_features = best_features[[1]]

#adding the target as the last column
best_features_target <- as.list(best_features)
best_features_target <- append(best_features_target, 'Depressed')
best_features_target <- as.character(best_features_target)
```

```{r}

#Setting up variables
targets = c('Depression', 'Anxiety')
groups = c('Group 1', 'Group 2', 'Group 3', 'Group 4', 'Group 5', 'Group 6', 'Group 7', 'Group 8')
plot_list = list()
  
i = 1
data_n = 1

#looping over targets

#looping over groups
for (group_n in groups){
print(paste('Group', data_n))
    
    
for (target_n in targets){
    
print(paste('Beginning', i))
    
#selecting the best subset of features
# its a lot of trouble convert it into the right format, but it works
best_features = as.character((df %>% filter(group == group_n) %>%
                                filter(target ==  target_n) %>%
                                select(feature_names)))
best_features = str_replace_all(best_features, '[[:punct:]]', "") %>% 
  str_replace_all('[\n]', '') %>% 
  str_replace_all('  ', ' ') %>% 
  str_replace_all('   ', ' ') %>% 
  str_replace_all('    ', ' ') %>% 
  str_replace_all('     ', ' ') %>% 
  str_replace_all('  ', ' ')
best_features = str_split(best_features, " ")
best_features = best_features[[1]]

#adding the target as the last column
best_features_target <- as.list(best_features)
best_features_target <- append(best_features_target, target_n)
best_features_target <- as.character(best_features_target)

print(best_features)

#subsetting the best_features + the target 
ku <- datasets[[data_n]] %>% 
  select(-c(Depressed,Anxiety)) %>% 
  rename(Depression = Depressed_F1,
         Anxiety = Anxiety_F2) %>% 
  #selecting the best features
  select(all_of(best_features_target))# %>% 
  #mutate_all(funs(ifelse(. == -1, 0, .)))

#make the partial correlation matrix
hep <- round(partial.r(data = ku,
                 x = best_features,
                 y = target_n, 
                 method = 'kendall'
                 )
             ,1)

#making the correlation plot
plot <- ggcorrplot(hep,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white",
           ggtheme = ggplot2::theme_minimal,
           lab = TRUE,
           show.legend = FALSE, 
           #tl.cex = 200/length(best_features_target),
           colors = c("#6D9EC1", "white", "#E46726")) #+
  #labs(title = paste(group_n, 'with target', target_n)) + 
  #theme(plot.title = element_text(size=18))

#appending the list of the plots
plot_list[[i]] = plot

#saving the ggplot as a png
filename = paste0("figures/words_as_predictors/correlation_matrix/", group_n, target_n, ".png")

#saving plots in different sizes to make them all readable  
#case_when(target_n == 'Anxiety' & group_nr == 'Group 6' ~ png(filename, width = 15, height = 15, units = 'in', res = 300),
#          target_n == 'Anxiety' & group_nr == 'Group 7' ~ png(filename, width = 15, height = 15, units = 'in', res = 300),
#          TRUE ~ png(filename, width = 10, height = 10, units = 'in', res = 300))


#making the size dependent on the number of words
size = 40*length(best_features_target)*0.01
  
png(filename, width = size, height = size, units = 'in', res = 300)

print(plot_list[[i]])
dev.off()

print(paste('End', i))
  
#appending to next plot
i = i + 1
} #finish group loop
#appending to next dataset  
data_n = data_n + 1   
}

#how to make tetrachoric correlations??
```


#Performance of best model

```{r}
depression <- df %>% 
  filter(target == 'Depression') %>% 
  filter(score == 'accuracy') %>% 
  group_by(group) %>% 
  summarize(accuracy = best_model_holdout_score) %>% 
  arrange(desc(accuracy)) %>% 
  ggplot() + 
  aes(x = desc(reorder(group,accuracy)), y = accuracy, fill = group) + 
  geom_bar(stat = 'identity') + 
  theme_minimal() + 
  labs(x='Group Number', y='Performance (Accuracy)', title='Depression') +
  ylim(0, 1) + 
  geom_text(aes(label = group),
            vjust = -0.3) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

anxiety <- df %>% 
  filter(target == 'Anxiety') %>% 
  group_by(group) %>% 
  filter(score == 'accuracy') %>% 
  summarize(accuracy = best_model_holdout_score) %>% 
  arrange(desc(accuracy)) %>% 
  ggplot() + 
  aes(x = desc(reorder(group,accuracy)), y = accuracy, fill = group) + 
  geom_bar(stat = 'identity') + 
  theme_minimal() + 
  labs(x='Group Number', y='Performance (Accuracy)', title='Anxiety') +
  ylim(0, 1) + 
  geom_text(aes(label = group),
            vjust = -0.3) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())


#png("figures/words_as_predictors/performance.png", width = 20, height = 10, units = 'in', res = 300)

depression / anxiety + 
  plot_layout(guides = 'collect') +
  plot_annotation(title='Performance of Best Models',
                  subtitle = 'Scoring Metric Accuracy')

#dev.off()

```

# Popularity of Best performing Models

```{r}
kek <- df %>% 
  group_by(best_model_name) %>% 
  tally() %>% 
  arrange(desc(n)) %>% 
  ggplot() + 
  aes(x = reorder(best_model_name, n), y = n, fill = best_model_name) + 
  geom_bar(stat = "identity") + 
  coord_flip() +
  labs(x= "remove x axis", y="Count", title = "Popularity of Best Performing Models") + 
  theme_minimal() + 
  theme(legend.position = 'none') +
  scale_fill_discrete(color_palette)

kek
```











